---
title: "Questionnaire Dashboard"
date:  "`r format(Sys.time(),format='%A %d %b %Y  %I:%M %p %Z')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    self_contained: true
    source_code: embed
    theme: default
    logo: ../../img/userlogo-small.png
---

```{=html}
<style collection="text/css">
.image-container {
background-position: center top !important;}
</style>
```

```{r setup-main, include=FALSE}
# Knitr options
knitr::opts_chunk$set(echo = FALSE, 
                      eval = TRUE,
                      warning = FALSE, 
                      message = FALSE, 
                      comment = NA, 
                      cache = FALSE)

# Load libraries
pacman::p_load(flexdashboard, fontawesome)
pacman::p_load(tidyverse, rio, labelled, lubridate)
pacman::p_load(crosstalk, reactable, reactablefmtr)
```

<!-- PAGE -->

# Consented {data-icon="fa-file-signature"}

<!-- 1st Column -->

## \#\# Column {data-width="200"}

### Mothers Pre-Screened

```{r}
valueBox(999, color = '#bfbfbf', caption = 'Mothers Pre-Screened', icon = "fa-users")
```

### Mothers Pre-Screen Eligible

```{r}
valueBox(888, color = '#fdbf6f', caption = 'Pre-Screen Eligible (Consented/Scheduled/Pending)', icon = "fa-user-friends")
```

### Mothers Consented

```{r}
valueBox(777, color = '#fb9a99', caption = 'Mothers Consented', icon = "fa-female")
```

### Mothers Terminated

```{r}
valueBox(6, color = '#fa8280', caption = 'Mothers Terminated', icon = "fa-user-times")
```

### Fathers Consented

```{r}
valueBox(555, color = '#a6cee3', caption = 'Fathers Consented', icon = "fa-male")
```

### Babies Born

```{r}
valueBox(444, color = '#b2df8a', caption = 'Babies Born', icon = "fa-child")
```

<!-- 2nd Column -->

## \#\# Column {.tabset}

### Consented (Figure)


```{r}

```


### Consented by **Site** (Figure)

```{r}

```

### Consented (Table)  {data-height="800"}

```{r}

```

### Reason(s) for ineligibility

```{r}

```

### Visits

```{r}

```

### Demographics  {data-height="800"}

```{r}

```

<!-- PAGE -->

# Mothers {data-navmenu="Questionnaire Status" data-icon="fa-female" data-orientation="columns"}

## Inputs {.sidebar}

```{r}
 dd <- import('dat/dat_m.rds')

dd_c <- import('dat/dat_m.rds') %>% 
   SharedData$new()

filter_select("SITENAME", "SITENAME", dd_c, ~SITENAME, multiple = FALSE)
filter_select("VISIT", "VISIT", dd_c, ~VISIT)
filter_select("FORMS", "FORMS", dd_c, ~COLLECTION)
filter_slider("MISSING", "% MISSING", dd_c, ~pct_miss, width = "80%", step = 1, ticks = FALSE)
```

## Column

```{r}
source('scr/create_reactable.r')
create_reactable(shared_data = dd_c, data = dd, collection = "Forms", total_footer = TRUE)
```


# Fathers {data-navmenu="Questionnaire Status" data-icon="fa-male" data-orientation="columns"}

```{r}

```

# Children {data-navmenu="Questionnaire Status" data-icon="fa-child" data-orientation="columns"}

```{r}

```
